---
title       : Stock Price Forecasting App
subtitle    : August 2015
author      : jshiju
job         : Freelance Consultant (Data Science)
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : [bootstrap, quiz]  # {mathjax, quiz, bootstrap}
mode        : standalone    # {selfcontained, standalone, draft}
knit        : slidify::knit2slides
---

## Stock Graphing and Forecasting 

1. Stock Price Forecasting App - using Shiny
2. Automatically pulls live data from Yahoo Finance
3. Graphs stock price and provides a prediction with confidence intervals
4. Selectable date ranges and forecast windows
5. Pick your desired confidence interval

--- .class #id 

## Demo

For example, suppose you want to decide if you sould invest your retirement funds in Apple stock.

1. You think the past 90 days are a good indicator of momentum in the next month
2. You want to be 95% confident in your forecast

``` {r LoadLibraries, echo = FALSE, results = 'hide', message = FALSE, warning = FALSE}

library (quantmod)
library (data.table)
```

``` {r SetParameters, echo = TRUE, results = 'hide', message = FALSE, warning = FALSE}

ticker <- "AAPL"
startDate <- Sys.Date() - 90
endDate <- Sys.Date()
data <- getSymbols (ticker, src = "yahoo", auto.assign = FALSE)
attr (data, "dimnames")[[2]] <- c ("Open", "High", "Low", "Close", "Volume", "Adjusted")
stock <- data [ (startDate <= index (data)) & (index (data) <= endDate) ]
forecastDays <- 30
confidence <- 95

```

--- .class #id 

## Sample Output

NOTE: The embedded code is avaiable at Github link provided at the last side.

``` {r Output, echo = FALSE, message = FALSE, warning = FALSE}

returns <- Delt (stock$Close)
meanReturn <- mean (returns, na.rm = TRUE)
sdReturn <- sd (returns, na.rm = TRUE)
qMult <- qnorm (0.5 + confidence/200)

predictClose <- as.numeric (tail (stock$Close, 1)) * (1 + meanReturn) ^ seq (1, forecastDays, by = 1)
predictHigh <- predictClose * (1 + sqrt (seq (1, forecastDays, by = 1)) * sdReturn * qMult)
predictLow <- predictClose * (1 - sqrt (seq (1, forecastDays, by = 1)) * sdReturn * qMult)

predict <- data.table (date = seq.Date (from = as.Date (endDate) + 1, to = as.Date (endDate) + forecastDays, by = 1),
                       Close = predictClose, High = predictHigh, Low = predictLow)

plot (x = index (stock), y = stock$Close, type = "l", col = "black",
      xlim = c (as.Date (startDate), max (as.Date (predict$date))),
      ylim = c (min (stock$Close, predictLow), max (stock$Close, predictHigh)),
      main = paste (ticker, " price and forecast"), xlab = "Date", ylab = "Price")
lines (x = predict$date, predict$Close,, lty = 1, col = "red")
lines (x = predict$date, predict$High, lty = 2, col = "red")
lines (x = predict$date, predict$Low, lty = 2, col = "red")
legend ("topleft", legend = c ("Close", "Predicted", paste (confidence, "% Confidence Interval")),
              col = c ("black", "red", "red"), lty = c (1, 1, 2))
```

* Disclaimer: This app is just for the demonstration of Slidify capabilities, and should not be used for trading decisions.

--- &radio

## Thank you!

A. Application: <https://jshiju.shinyapps.io/devdataprod> <br>
B. Source: <https://github.com/jshiju/devdataprod> <br>
C. Presentation : <http://rpubs.com/jshiju/103048> <br>

Please share your feedback on the product!!

1. _1_  (Okay)
2. _2_  (Good)
3. _3_  (Very Good)
4. _4_  (Excellent)


*** .hint
Please try out the app at Rstudio Shinyapps.io !!

*** .explanation
Thank you for your feedback and support.


